Super awesome embeddings

### 2019-02-03 paper/main.tex
Minor changes, add link to repo

Examples were mostly gathered from Wikipedia, using \textit{What links here} utility for each keyword. If usage examples
from Wikipedia were not enough, other websites were used (or even the Wiki article on specific keyword itself).

@@

\bigskip
The correct keyword for each example, together with a path to file and link, where the original text was taken from,
are stored in CSV files: \textit{train.csv} for training set, \textit{test.csv} for test set. Keywords themselves,
together with links to their Wiki articles, are stored in \textit{keywords.csv} file.

>>>>

Examples were mostly gathered from Wikipedia, using \textit{What links here} utility for each keyword.
If usage examples from Wikipedia were not enough, other websites were used (or even the Wikipedia article on specific keyword itself).

@@

\bigskip
The correct keyword for each example, together with a path to file and a link, where the original text was taken from, are stored in CSV files: \textit{train.csv} for training set, \textit{test.csv} for test set (columns: path,keyword,link).
Keywords themselves, together with links to their Wikipedia articles, are stored in \textit{keywords.csv} file.
Dataset, together with the code to execute experiments from this paper, can be found on our GitHub repository \cite{repository}.
